\documentclass[../main.tex]{subfiles}
\begin{document}

\begin{description}[style=unboxed,leftmargin=0pt]
  \item[Fuzzy hashing function] Function producing similar hashes for similar inputs.
  \item[Ethereum] The computer network running the EVM.
  \item[EVM] Ethereum Virtual Machine. There is one EVM with one state. Transactions change the state.
  \item[Blockchain] Complete record of all transaction.
  \item[Transaction] Can change account balances, call smart contract functions or deploy smart contracts.
  \item[Ethereum account] Accounts are uniquely identified by there 20 byte address, have an Ether balance and can execute transactions.
  \item[Ether] Currency used to pay for the execution of transactions.
  \item[Smart Contract] An Ethereum account with associated runnable code and data stored on the EVM. Can refer to just the runtime code or the source code or the semantics of the contract interface.
  \item[Contract interface] Smart Contract have a Set of contract functions callable by other accounts via message or transaction.
  \item[Contract function] Can change account data and Ether balances and call functions of the same of other contracts via messages.
  \item[Meassage] Smart contracts can call other contracts functions via messages. Unlike transactions and logs, these messages are not stored on the blockchain.
  \item[Logs] Smart contracts can create logs, which are stored on the blockchain and can therefore easily be observed and referenced. Decentralized applications are implemented using logs.
  \item[Runtime code] The runnable code stored on the EVM as a sequence of opcodes. Used synonymously with code or bytecode.
  \item[Deployment code] Runs once and stores the runtime code.
  \item[Opcode] An EVM instruction encoded as one byte.
  \item[Levenshtein distance] Also called edit distance. The minimum number of inserts, deletions and substitutions necessary to change one string into the other.
  \item[Levenshtein similarity] \( similarity(a, b) = 1 - distance(a, b) / max\{|a|, |b|\} \in [0,1] \). \label{lev_sim}
  \item[Jaccard index] \(J(A,B) = |A \cap B| / |A \cup B| \in [0,1]\)
  \item[ABI] Standard encoding of the Contract interface.
  \item[Function signature] String containing function name and parameters types.\\E.g.: \code{deposit(uint256,address)}
  \item[Fourbyte signature] Function signature hashed to a 4-byte value.
  \item[solc] Standard Solidity compiler.
  \item[Solidity] Most common and original smart contract language.
\end{description}

\end{document}
